---
title: "Notlar"
format: html
---

You can find all your quiz and midterm scores. Your assignment score is explained in second table below. For attendance score, if you attended 12 lectures you got 5 points and you missed 1 point for each missed lecture.

## All scores

```{r}
#| echo: false
#| warning: false
library(gt)

readr::read_csv("notlar-publish.csv") |>
gt() |>
cols_align(
  align = c("center"),
  columns = everything()
) |>
sub_missing(
  columns = everything(),
  rows = everything(),
  missing_text = "-"
)
```

## Poster assignment evaluation chart

There are five items in evaluation, each score 2 points. 

- If you submitted draft figures, you got 2 points
- If you have poster qmd file, you got 2 points
- If your qmd file renders successfully you got 2 points
- If your poster has at least 3 figures, you got 2 points
- If your poster has meaningful context and story you got 2 points. 

```{r}
#| echo: false
#| warning: false
library(gt)

readr::read_csv("notlar-poster.csv") |>
gt() |>
cols_align(
  align = c("center"),
  columns = everything()
) |>
sub_missing(
  columns = everything(),
  rows = everything(),
  missing_text = "-"
)
```
